\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/appendix.tex
update plots
cleanup
nature bibstyle

\begin{figure}
    \centering
    \includegraphics{figures/flesch_kincaid_reading_ease.pdf}
    \caption{\textbf{Distribution of Flesch-Kincaid reading ease scores of the questions.} The Flesch-Kincaid reading ease score\cite{flesch1948new} is a measure of how easy a text is to read. It is calculated based on the average number of syllables per word and the average number of words per sentence. The higher the score, the easier the text is to read. The distribution of the scores of the questions is shown in the histogram. }
    \label{fig:flesch_kincaid_reading_ease}
\end{figure}

@@

\begin{figure}
    \label{fig:barplot_all_correct_all_questions}
\end{figure}

@@

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/flesch_kincaid_reading_ease.pdf}
    \caption{\textbf{Distribution of Flesch-Kincaid reading ease scores of the questions.} The Flesch-Kincaid reading ease score\cite{flesch1948new} is a measure of how easy a text is to read. It is calculated based on the average number of syllables per word and the average number of words per sentence. The higher the score, the easier the text is to read. The distribution of the scores of the questions is shown in the histogram. }
    \label{fig:flesch_kincaid_reading_ease}
    \script{wordcloud.py}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/question_count_barplot_mcq_vs_general.pdf}
    \caption{\textbf{Number of multiple choice questions vs.\ open-ended questions per topic.} The bar plot shows the number of multiple choice questions and general questions per topic.}
    \script{plot_statistics.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/overall_performance.pdf}
    \caption{\textbf{Overall performance of the models on the \chembench corpus.} The bar plot shows the fraction of questions that were answered completely correctly by the models. Scores computed on the entire \chembench corpus.}
    \label{fig:barplot_all_correct_all_questions}
    \script{plot_overview_performance_plot.py}
\end{figure}

@@

\printnoidxglossary[type=\acronymtype]  % https://github.com/tectonic-typesetting/tectonic/issues/704

### 2024-03-19 src/tex/ms.tex
nature bibstyle

\begin{figure}
    \centering
    \includegraphics{figures/confidence_vs_performance_overall.pdf}
    \caption{\textbf{Relationship between confidence of the model in the answer and correctness.} For this analysis, we used verbalized confidence estimates from the model. To obtain those estimates, we prompted the models to return a confidence score on an ordinal scale. We then plot the correctness of the answers (which can be either completely correct or completely incorrect) against the confidence score.
        The stripplots show the individual data points, the lines show the mean.}
    \label{fig:confidence_vs_performance}
    \script{joint_analysis_confidence_performance.py}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/confidence_vs_performance_overall.pdf}
    \caption{\textbf{Relationship between confidence of the model in the answer and correctness.} For this analysis, we used verbalized confidence estimates from the model. To obtain those estimates, we prompted the models to return a confidence score on an ordinal scale. We then plot the correctness of the answers [which can be either completely correct (1) or completely incorrect (0)] against the confidence score.
        The stripplots show the individual data points, the lines show the mean and the errorbars show the standard error of the mean. The figure shows that the reliability of the confidence estimates varies widely across models. While the ones for GPT-4 and Claude-2 are not particularly reliable, the ones for Claude-3 follow the expected trend.}
    \label{fig:confidence_vs_performance}
    \script{joint_analysis_confidence_performance.py}
\end{figure}
